A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-06-25 nips2015.tex
fixups + more

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item[--] avoid having to compute the projections $\proj_{Q_k}$,
\item[--] have control over how far we are from the set of equilibria and
  avoid infinite (and thus non-informative) primal-dual gaps
\end{itemize}

@@

\section{Conclusion}
Making use of the sequence-form representation
\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
deviced a primal-dual algorithm for computing Nash equilibria in
two-person zero-sum sequential games with imcomplete information (like
Texas Hold'em, etc.). Our algorithm is simple to implement, with a
very low constant cost per iteration, and enjoys a rigorous
convergence theory with a proven $\mathcal{O}(1/min(\rho,\epsilon))$ convergence
in terms of basic operations (matvec products, clipping, etc.), to a
Nash $(\rho,\epsilon$-equilibrium of the game.
Equilibrium problems are saddle-point convex-concave problems, and as
such a natural choice for an algorithm would be in the family of
primal-dual algorithms. The author believes such primal-dual schemes
will receive more attention in the algorithmic game theory community
in future.

>>>>

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item[--] avoid having to compute the projections $\proj_{Q_k}$,
\item[--] have control over how far we are from the set of equilibria and
  avoid infinite (and thus non-informative) primal-dual gaps.
\end{itemize}

@@

\section{Conclusion}
Making use of the sequence-form representation
\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
deviced a primal-dual algorithm for computing Nash equilibria in
two-person zero-sum sequential games with imcomplete information (like
Texas Hold'em, etc.). Our algorithm is simple to implement, with a
very low constant cost per iteration, and enjoys a rigorous
convergence theory with a proven $\mathcal{O}(1/min(\rho,\epsilon))$ convergence
in terms of basic operations (matvec products, clipping, etc.), to a
Nash $(\rho,\epsilon)$-equilibrium of the game.

Equilibrium problems are saddle-point convex-concave problems, and as
such a natural choice for algorithms for solving them would be in the
family of primal-dual algorithms. The author believes such primal-dual
schemes will receive more attention in the algorithmic game theory
community in future.
